%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {Infodat}{Houston, TX}
    {Software Developer}{January 2024 – Present}
    \resumeItemListStart
        \resumeItem{\textbf{Technologies:} TypeScript, Angular, HTML, CSS}

        \resumeItem{Enhanced code maintainability and facilitated efficient unit testing by implementing modularized Angular components.}

        \resumeItem{Achieved an 80\% test coverage, ensuring the reliability and stability of the application.}
        
    \resumeItemListEnd

    \resumeSubSubheading
    {Software Developer Intern}{May 2023 – December 2023}
    \resumeItemListStart
        \resumeItem{\textbf{Technologies:} TypeScript, React, HTML, CSS, Jest}

        % \resumeItem{Optimized the internal assessment process for over 100 employees by developing a web application using React.}
        \resumeItem{Developed and maintained a web application to streamline internal assessment process, ensuring code quality and architecture.}

        \resumeItem{Achieved a 50\% reduction in manual testing by implementing unit and integration tests utilizing Jest.}
        
        \resumeItem{Drove cross-functional collaboration using Git and Azure DevOps, enhancing team efficiency and project management.}
    \resumeItemListEnd

    \resumeSubheading
    {University of Houston}{Houston, TX}
    {Teaching Assistant | COSC-2436 Programming and Data Structures}{August 2022 – May 2023}
    \resumeItemListStart
        \resumeItem{Designed and executed a comprehensive curriculum including hands-on programming activities and assessments.} 

        \resumeItem{Facilitated lab sessions emphasizing practical application of data structures and algorithms in C++.} 

        % \resumeItem{Mentored and supported students in data structure concepts, improving test scores significantly.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Mainbridge Health Partners}{Vietnam}
    {Software Engineer Intern}{December 2022 – April 2023}
    \resumeItemListStart    
        \resumeItem{\textbf{Technologies:} C\#, ASP.NET MVC, Microsoft SQL Server, HTML, CSS}  

        % \resumeItem{Developed a management system for patients to oversee their appointments and offered healthcare providers and administrative staff essential tools for streamlined healthcare delivery.} 
        \resumeItem{Optimized patient and staff workflows and enhanced interdepartmental coordination efficiency by developing modular UI components.} 
        
        % \resumeItem{Enhanced interdepartmental coordination efficiency by 20\% through modular UI component development for different roles.} 
    
        % \resumeItem{Integrated multiple core features, including appointment booking, user authentication, and data reporting, to optimize hospital operations and enable analytical capabilities.} 
        \resumeItem{Developed new features and expanded functionality on existing web application, involving both front-end and back-end tasks which resulted in better user experience.} 
    
    \resumeItemListEnd

    
\resumeSubHeadingListEnd