%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Fuel Quote Generator} $|$ \emph{JavaScript, React.js, Express.js, JWT, MySQL, HTML, CSS}}{}
    \resumeItemListStart
        \resumeItem{Developed a full-stack application for generating fuel quotes using client location, purchase history, requested gallons, and company profit margin as inputs.}

        \resumeItem{Strengthened application security through the implementation of JWT authentication, ensuring data confidentiality.}
        
        \resumeItem{Accomplished a 30\% reduction in development time by collaborating with a team of 4 members and following agile methodologies.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Amusement Park Website} $|$ \emph{C\#, ASP.NET Core, MySQL, HTML, CSS, Azure}}{}
    \resumeItemListStart
        \resumeItem{Collaborated with a team of 5 to develop a web application facilitating trip planning, ticket purchases, and company system management tools.}
        
        \resumeItem{Led backend development, creating a robust set of API endpoints, conducting data analysis, and integrating database systems into the application.}

        \resumeItem{Deployed and managed the live application on Azure while efficiently troubleshooting database and API issues.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Data-Driven Cardiovascular Analysis and Insights} $|$ \emph{R}}{}
    \resumeItemListStart
        \resumeItem{Analyzed a comprehensive dataset of 70,000+ accounts, utilizing machine learning techniques including logistic regression, and decision tree to investigate factors contributing to cardiovascular health outcomes.}  

        \resumeItem{Applied logistic regression to predict the presence of cardiovascular disease, leveraging interpretable results to understand the impact of variables such as age, height, weight, blood pressure, and cholesterol.} 
    \resumeItemListEnd    
\resumeSubHeadingListEnd